upwell_IDX

### 2019-08-09 upwell_IDX.Rmd
fixed

upwell_MCS <- ggplot(data = match, aes(x = t, y = temp)) +
  geom_line() +
  geom_point(data = filter(match, event == TRUE), colour = "navy") +
  geom_rug(data = filter(match, ui.saws == TRUE), sides = "b") +
  scale_x_date(expand = c(0, 0)) +
  facet_wrap(~site, ncol = 1) +
  theme_grey() +
  labs(y = "Temperature (°C)", x = NULL)
upwell_MCS
```

>>>>

upwell_MCS <- ggplot(data = match, aes(x = t, y = ui.saws)) +
  geom_line() +
  geom_point(data = filter(match, event == TRUE), colour = "navy") +
  geom_rug(data = filter(match, saws.condition == "upwelling"), sides = "b") +
  scale_x_date(expand = c(0, 0)) +
  facet_wrap(~site, ncol = 1) +
  theme_grey() +
  labs(y = "Temperature (°C)", x = NULL)
upwell_MCS
